\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package
\usepackage{hyperref}
% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna (+49) 176 34650070}  % Phone number
  \item {\Calluna \href{mailto:judadi1994@gmail.com}{judadi1994@gmail.com}}   % E-mail address
  \item {\Calluna \href{hhttps://juliandiaz.web.app/}{https://juliandiaz.web.app/}}  % Website / Portfolio
    \item {\Calluna Berlin, Germany}  % Website / Portfolio
\end{flushright}\vspace{-54pt}

\begin{flushleft}
  {\Calluna \fontsize{30pt}{30pt}\selectfont \textsc{Julian Diaz}} 
  \\
  {\Calluna \fontsize{14pt}{14pt}\selectfont \textsc{Software Developer}}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}
% -------------------- WORK EXPERIENCE --------------------
\sectionBlock{
\section{Work Experience}
}{
\eduHeading
  {Konnektaro}{Berlin, Germany}
  {\textbf{Co-Founder}}{2025.05 -- Present}
\itemListStart
  \myItem{Developed a mobile-first progressive web app for real-time learning sessions using \textbf{React}, \textbf{Next.js}, and \textbf{TypeScript}.}
  \myItem{Implemented \textbf{Firebase Authentication} (Google and anonymous login) with secure token handling across frontend and backend.}
  \myItem{Built \textbf{RESTful APIs} with \textbf{Node.js} and \textbf{Express}, managing complex user interactions, event-based sessions, and partner pairing logic.}
  \myItem{Designed and integrated modular UI using \textbf{Tailwind CSS} optimized for mobile experience and reusability.}
  \myItem{Structured and maintained a \textbf{MongoDB} database ensuring scalable and efficient data access.}
  \myItem{Integrated a self-hosted \textbf{speech-to-text} service using \textbf{OpenAI Whisper}, exposing it through a custom AI API for real-time and cost-free transcription within learning sessions.}
\itemListEnd

\eduHeading
  {EduEnvire}{Copenhagen, Denmark (Remote)}
  {\textbf{Founding Engineer | Technical Advisor}}{2024.03 -- 2024.12}
\itemListStart
  \myItem{Led the design of a check-in system allowing students to register attendance while giving teachers real-time insights into device usage.}
  \myItem{Collaborated with backend engineers to define app architecture and data mapping strategies.}
  \myItem{Developed frontend for both web and mobile apps using \textbf{React TS} and \textbf{React Native (Expo)}.}
  \myItem{Implemented CI/CD pipelines for the frontend, ensuring smooth alpha testing phases.}
      \vspace{-10pt} 
  \myItem{Mentored founders on technical aspects of starting their business.}

\itemListEnd

\eduHeading
  {Iomoto}{Berlin, Germany}
  {\textbf{Frontend Engineer}}{2020.05 -- 2023.12}
\itemListStart
  \myItem{\textbf{Project: B2C Automotive Sales App (Flutter, Dart)}}
\begin{itemize}[label=$\circ$]
    \item Built EV simulation tools to compare costs, charging, and mileage with fossil-fueled vehicles.
    \item Created the \textbf{Garage feature} synced with commuter habits and developed login flow with focus on accessibility/security.
    \item Conducted unit testing for Flutter and contributed to main app maintenance.
  \end{itemize}

  \myItem{\textbf{Project: B2B Truck Fueling \& Fleet Management Tool (React, Azure)}} 
\begin{itemize}[label=$\circ$]
    \item Developed platform using \textbf{React (JavaScript)}, HTML, CSS with authentication via \textbf{Azure AD B2C}. 
    \item Ensured fleet management for 5000+ vehicles and delivered white-label solution with CI/CD pipelines.
    \item Implemented automated tests (\textbf{Jest}, \textbf{Cypress}) and maintained codebase in GitLab under Agile practices.
  \end{itemize}
\itemListEnd

\eduHeading
  {The Key Technology}{Germany}
  {\textbf{Frontend Engineer, Intern}}{2019.11 -- 2020.01}    
\vspace{10pt} 

\eduHeading
  {Virtual Media Network}{Colombia}
  {\textbf{Multimedia Designer}}{2017.08 -- 2017.12}
\vspace{10pt} 

\eduHeading
  {Avantel}{Colombia}
  {\textbf{Multimedia Designer, Intern}}{2016.08 -- 2017.01}
}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {Leeds Beckett University}{Leeds, UK}
  {M.Sc. in Creative Technologies}{2017 -- 2019}
\itemListStart
  \myItem{\textbf{Thesis:} AR-AI Navigation in Indoor Spaces. Developed a navigation system with \textbf{C\#}, \textbf{JavaScript}, and the \textbf{Unity} engine.}
\itemListEnd
\eduHeading
  {Universidad Militar}{Bogota, Colombia}
  {B.Eng. in Multimedia Engineering}{2012 -- 2017}
  \vspace{30pt} 
}
% -------------------- SKILLS --------------------
\sectionBlock{
\section{Skills}
}{
\skillListStart
\justifying
\item \emph{Languages \& Frameworks}: React, Flutter, JavaScript, TypeScript, Dart, HTML, CSS, C\#, ActionScript
\item \emph{Tools \& Platforms}: MongoDB, Node.js, Express, Firebase, Azure DevOps, Git, CI/CD, Figma, Notion, Jira
\item \emph{Design \& Multimedia}: Illustrator, Photoshop, Adobe After Effects, Adobe Animate, Unity
\skillListEnd
}
% -------------------- ABILITIES --------------------
\sectionBlock{
\section{Abilities}
}{
\skillListStart
\justifying
\item Stakeholder Management, Clean Code Practices, Attention to Detail
\item Creative Thinking, Fast Learning, Project Management
\item Problem Solving, Mentoring and Teaching
\skillListEnd
}
% -------------------- LANGUAGES --------------------
\sectionBlock{
\section{Languages}
}{
\skillListStart
\justifying
\item Spanish (Native), English (Fluent), German (B1)
\skillListEnd
}

\end{document}
